---
title: "events_fighter"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
# event results
library(rvest)
library(tidyverse)
library(glue)
```


```{r}
Sys.Date()
```


Get all tables

```{r}
url <- "https://www.sherdog.com/fighter/Justin-Gaethje-46648"
read_html(url) %>% html_nodes("table") %>% html_table()
```

Get specific table.

```{r}
read_html(url) %>% html_nodes("body > div.container > div:nth-child(3) > div.col_left > section:nth-child(4) > div > div.content.table") %>% html_children() %>% html_table(header = TRUE) %>% as.data.frame() -> sample_table
```

```{r}
seed_div <- read_html(url) %>% html_nodes("td:nth-child(2) a , .cnaccept") %>% html_attr(.,"href") %>% as.data.frame() %>% unique()
names(seed_div)[1]<-"fighterName"
rownames(seed_div)<-str_split(seed_div$fighterName,"/",simplify = TRUE)[,3]
```


# Create Seed Crawler
```{r}
# create seed crawler function

seed_crawler <- function(url){
  base_url <- "https://www.sherdog.com/fighter/"
    fighter_url <- glue(base_url,"{url}")
    
  tmp_seed<-read_html(fighter_url) %>% 
    html_nodes("td:nth-child(2) a , .cnaccept") %>% 
    html_attr(.,"href") %>% as.data.frame() %>% 
    unique()
}


```


Create Division Crawler

```{r}
fighter_crawler <- function(url){
    base_url <- "https://www.sherdog.com"
    fighter_url <- glue(base_url,"{url}")
    
    tmp <-read_html(fighter_url) %>% html_nodes("td:nth-child(2) a , .cnaccept") %>% html_attr(.,"href") %>% as.data.frame()
    nam<-paste0(fighter_url,"_")
    assign(nam,tmp)
}
```


Test Division Crawler 155lbs

```{r}
seed <- seed_div %>% slice_head(n=31)

map_df(seed$fighterName,fighter_crawler) %>% unique %>% rowid_to_column() -> div_lightweights 
names(div_lightweights)[2]<-"fighterName"
```


Create Results Crawler

```{r}
url_crawler <- function(fighter){
  base_url <- "https://www.sherdog.com"
  
  full_url <- glue(base_url,"{fighter}")
  
  read_html(full_url) %>% 
    html_nodes("body > div.container > div:nth-child(3) > div.col_left > section:nth-child(4) > div > div.content.table") %>% html_children() %>% 
    html_table(header = TRUE, fill=TRUE) %>% 
    as.data.frame()
}

```

Test Results Crawler

```{r}
url_crawler("/fighter/Khabib-Nurmagomedov-56035") -> sample_results

```

Execute over the entire 155lb division. 

```{r}
map_df(div_lightweights$fighterName, url_crawler,.id = "rowid") -> results_lightweights
```

```{r}
write.csv(div_lightweights,paste0(Sys.Date(),"_","div_lightweights.csv"))
write.csv(results_lightweights,paste0(Sys.Date(),"_","results_lightweights.csv"))
```

OPERATIONAL

# Pass Division Seeds For Multiple Divisions
```{r}
url <-c(
        "Ricky-Simon-111209","Umar-Nurmagomedov-240893",
        "Alexander-Volkanovski-101527","Max-Holloway-38671",
        "Justin-Gaethje-46648","Khabib-Nurmagomedov-56035",
        "Neil-Magny-69166","Trevin-Giles-111237")

map_df(url,seed_crawler) ->out

names(out)[1]<-"fighterName"

# for fighter who moved across a division
out %>% unique() ->out
rownames(out)<-str_split(out$fighterName,"/",simplify = TRUE)[,3]
```

# Execute Fighter Crawler
```{r}
map_df(out$fighterName,fighter_crawler) %>% unique %>% rowid_to_column() -> div_135_145_155_170_185 
names(div_135_145_155_170_185)[2]<-"fighterName"
```


```{r}
urls <-   c("http://www.amazon.com",
            "http://this.isafakelink.biz",
            "https://stackoverflow.com")

url_in<-div_135_145_155_170_185$fighterName[3000:3125]


valid_url <- function(url_in,t=2){
    
  base_url <- "http://www.sherdog.com"
  con <- glue(base_url,"{url_in}")
  con <- url(con)
  check <- suppressWarnings(try(open.connection(con,open="rt",timeout=t),silent=T)[1])
  suppressWarnings(try(close.connection(con),silent=T))
  ifelse(is.null(check),TRUE,FALSE)
}

sapply(url_in,valid_url) ->valid_list
```
```{r}
library(rex)
valid_chars <- rex(except_some_of(".", "/", " ", "-"))

re <- rex(
  start,

  # protocol identifier (optional) + //
  group(list("http", maybe("s")) %or% "ftp", "://"),

  # user:pass authentication (optional)
  maybe(non_spaces,
    maybe(":", zero_or_more(non_space)),
    "@"),

  #host name
  group(zero_or_more(valid_chars, zero_or_more("-")), one_or_more(valid_chars)),

  #domain name
  zero_or_more(".", zero_or_more(valid_chars, zero_or_more("-")), one_or_more(valid_chars)),

  #TLD identifier
  group(".", valid_chars %>% at_least(2)),

  # server port number (optional)
  maybe(":", digit %>% between(2, 5)),

  # resource path (optional)
  maybe("/", non_space %>% zero_or_more()),

  end
)
```

```{r}

url_in<-div_135_145_155_170_185$fighterName

construct_url <- function(url){
    
  base_url <- "https://www.sherdog.com"
  con <- glue(base_url,"{url}")
}

construct_url(url_in) -> urls_check 
```

```{r}
all(grepl(re, urls_check) == TRUE)
```


# Execute Results Crawler

```{r}
start<- Sys.time()
b1500 <- div_135_145_155_170_185$fighterName[1001:1500]
map_df(b1500, url_crawler,.id = "rowid") -> results_b1500
end <-Sys.time()
end-start
```

# Data Preparation

```{r}
library(stringr)

results_135_145_170 -> working_copy
```

```{r}
div_135_145_170 %>%  mutate(Opponent = str_trim(str_replace_all(str_remove_all(str_split(fighterName,"fighter/",simplify = TRUE)[,2],"[0-9]"),"-"," "))) -> div_135_145_170
```

```{r}
working_copy %>% select(rowid:Time) %>% 
  mutate(Method=str_c(str_split(Method.Referee,"[)]",simplify = TRUE)[,1],")")) %>% 
  select(-Method.Referee) %>% rename(Round = R) %>% 
  na.omit -> working_copy
```

Extract Dates of Events
```{r}
working_copy %>% mutate(DateEvent= as.Date(str_replace_all(str_replace_all(str_sub(working_copy$Event,start = -15),"/","-")," ",""),format = "%b-%d-%Y")) -> working_copy

str_sub(working_copy$Event,start=-15) <-""
```

Calculate Streaks - Prepare

```{r}
working_copy[order(working_copy$DateEvent),] %>% 
  group_by(rowid) %>% 
  mutate(Outcome = case_when(Result=="win" ~ 1, TRUE ~0)) %>% 
  mutate(lagged = lag(Outcome)) %>% mutate(start=(Outcome != lagged)) -> working_copy

working_copy %>% mutate(start=replace_na(start,TRUE)) -> working_copy

working_copy %>% mutate(streak_id = cumsum(start)) ->working_copy

```
Calculate Streak Length and Arrange


```{r}
working_copy %>%  group_by(rowid,streak_id) %>% 
  mutate(streak=row_number()) %>% 
  ungroup() %>% 
  arrange(.,rowid,DateEvent) %>% 
  rename(PreviousOutcome=lagged) -> working_copy
```

Previous Result

```{r}
working_copy %>% group_by(rowid) %>% mutate(StreakLength = lag(streak)) %>% 
  mutate(StreakLength = case_when(PreviousOutcome == 0 ~ -StreakLength, TRUE ~ StreakLength)) -> working_copy
```

Win Ratio

```{r}
working_copy %>% ungroup() %>% group_by(rowid) %>%  
  mutate(WinRatio = lag(cumsum(Outcome))/(row_number()-1)) %>% 
  mutate(CountFights =row_number()-1) ->working_copy
```

Finish Ratio and Finish Previous

```{r}
working_copy %>% mutate(FinishRatio = lag(!str_detect(Method,"Decision") & Outcome == 1)) %>%
  mutate(FinishRatio=replace_na(FinishRatio,FALSE)) %>% 
  mutate(FinishRatio = cumsum(FinishRatio)/(CountFights)) %>% 
  mutate(FinishPrevious = case_when(!str_detect(Method,"Decision") & Outcome == 1 ~TRUE, TRUE ~ FALSE)) %>% 
  mutate(FinishPrevious=lag(FinishPrevious)) -> working_copy
```

Finished Ratio and Finished Previous

```{r}
working_copy %>% mutate(FinishedRatio = lag(!str_detect(Method,"Decision") & Outcome == 0)) %>% mutate(FinishedRatio = replace_na(FinishedRatio,FALSE)) %>% 
  mutate(FinishedRatio = cumsum(FinishedRatio)/(CountFights)) %>% 
  mutate(FinishedPrevious = case_when(!str_detect(Method,"Decision") & Outcome == 0 ~TRUE, TRUE ~ FALSE)) %>% 
  mutate(FinishedPrevious = lag(FinishedPrevious)) -> working_copy
```

```{r}
working_copy %>% mutate(FinishedTrue = lag(!str_detect(Method,"Decision") & Outcome == 0)) %>% mutate(FinishedTrue = replace_na(FinishedTrue,FALSE)) %>% 
  mutate(FinishedCount=cumsum(FinishedTrue)) %>% 
  mutate(FinishTrue = lag(!str_detect(Method,"Decision") & Outcome == 1)) %>% mutate(FinishTrue = replace_na(FinishTrue,FALSE)) %>% 
  mutate(FinishCount=cumsum(FinishTrue)) %>% 
  mutate(DamageDiff = FinishCount/(FinishedCount+1)) %>% select(c(-FinishedTrue,-FinishTrue)) -> working_copy

```

```{r}
desPath <- as.character(Sys.Date())
setwd("C:/Users/eoedd/Desktop/locstore/projects/_octagon/data")
dir.create(desPath)
setwd(paste0("C:/Users/eoedd/Desktop/locstore/projects/_octagon/data","/",desPath))
write.csv(working_copy,"result-metrics.csv")
```


# Build Results Matrix

Join to Get Fighter Name

```{r}
working_copy %>% mutate(rowid = as.integer(rowid)) -> working_copy_x

div_135_145_170 %>% rename(Fighter = Opponent) -> div_135_145_170

working_copy_x %>% left_join(div_135_145_170,by="rowid") ->working_copy_x

working_copy_x %>% rename(Fighter=Fighter.y, Opponent=Fighter.x) -> working_copy_x

```

Reset for Opponent Id

```{r}
div_135_145_170 %>% rename(Opponent = Fighter) -> div_135_145_170
```

Join For Opponent Id

```{r}
working_copy_x %>% left_join(div_135_145_170,by="Opponent") -> working_copy_x

working_copy_x %>% rename(FighterId = rowid.x, OpponentId = rowid.y) -> working_copy_x

```
Remove Unnecessary Columns

```{r}
working_copy_x %>% select(-fighterName.x,-fighterName.y) -> working_copy_x
```

Join For Composite

```{r}
working_copy_x %>% 
  mutate(FighterComposite = str_c(working_copy_x$FighterId,
                                  working_copy_x$Opponent,
                                  working_copy_x$DateEvent,sep = "_"),
        OpponentComposite = str_c(working_copy_x$OpponentId,
                                  working_copy_x$Fighter,
                                  working_copy_x$DateEvent,sep = "_")) ->working_copy_x 
```

Make Copies for Self Join
```{r}
working_copy_x -> working_copy_y
```


Join for Result Set

```{r}
working_copy_x %>% left_join(working_copy_y,by=c("FighterComposite"="OpponentComposite")) -> raw_event_results
```

```{r}
setwd(paste0("C:/Users/eoedd/Desktop/locstore/projects/_octagon/data","/",desPath))
write.csv(raw_event_results,"raw-event-results.csv")
```

Unduplicate resultset

Derive a column to further distinguish outcomes on events
```{r}
# the same for both rows
# ads uniqueness to results which finish in the same way on the sam e card i.e. decisions
raw_event_results %>% mutate(IdKey = FighterId.x+FighterId.y) -> raw_event_results
```


```{r}
raw_event_results[!duplicated(raw_event_results[c("Event.x","Round.x","Time.x","Method.x","IdKey")]),] -> unique_event_results
```


Filter down to reflect only complete cases

```{r}
unique_event_results %>% filter(complete.cases(.)) -> complete_event_results
setwd(paste0("C:/Users/eoedd/Desktop/locstore/projects/_octagon/data","/",desPath))
write.csv(complete_event_results,"complete-event-results.csv")
```
Derived Additional Model Parameters
```{r}
complete_event_results %>% mutate(delta_FP=FinishPrevious.x-FinishPrevious.y,
                    delta_FIP=FinishedPrevious.x-FinishedPrevious.y,
                    delta_FC=FinishCount.x-FinishCount.y,
                    delta_FIC=FinishedCount.x-FinishedCount.y) ->modelset_derived

setwd(paste0("C:/Users/eoedd/Desktop/locstore/projects/_octagon/data","/",desPath))
write.csv(modelset_derived,"model-input-full.csv")
```

Define Dataset

```{r}
modelset_derived %>% select(Result.x,
                    Method.x,
                    Fighter.x,
                    Opponent.x,
                    CountFights.x,
                    PreviousOutcome.x,
                    StreakLength.x,
                    WinRatio.x,
                    FinishRatio.x,
                    FinishPrevious.x,
                    FinishedRatio.x,
                    FinishPrevious.x,
                    FinishCount.x,
                    FinishedCount.x,
                    DamageDiff.x,
                    CountFights.y,
                    PreviousOutcome.y,
                    StreakLength.y,
                    WinRatio.y,
                    FinishRatio.y,
                    FinishPrevious.y,
                    FinishedRatio.y,
                    FinishPrevious.y,
                    FinishCount.y,
                    FinishedCount.y,
                    DamageDiff.y,
                    delta_FP,
                    delta_FIP,
                    delta_FC,
                    delta_FIC) ->modelset_selected

setwd(paste0("C:/Users/eoedd/Desktop/locstore/projects/_octagon/data","/",desPath))
write.csv(modelset_selected,"model-input-standard.csv")
```







Data Preparation


```{r}
library(stringr)

results_lightweights -> wc
```

```{r}

div_lightweights %>%  mutate(Opponent = str_trim(str_replace_all(str_remove_all(str_split(fighterName,"fighter/",simplify = TRUE)[,2],"[0-9]"),"-"," "))) -> div_lightweights
```


```{r}

wc %>% select(rowid:Time) %>% 
  mutate(Method=str_c(str_split(Method.Referee,"[)]",simplify = TRUE)[,1],")")) %>% 
  select(-Method.Referee) %>% rename(Round = R) %>% 
  na.omit -> wc
```

Extract Dates of Events

```{r}
wc %>% mutate(DateEvent= as.Date(str_replace_all(str_replace_all(str_sub(wc$Event,start = -15),"/","-")," ",""),format = "%b-%d-%Y")) -> wc

str_sub(wc$Event,start=-15) <-""
```

Calculate Streaks - Prepare

```{r}

wc[order(wc$DateEvent),] %>% 
  group_by(rowid) %>% 
  mutate(Outcome = case_when(Result=="win" ~ 1, TRUE ~0)) %>% 
  mutate(lagged = lag(Outcome)) %>% mutate(start=(Outcome != lagged)) -> wc

wc %>% mutate(start=replace_na(start,TRUE)) -> wc

wc %>% mutate(streak_id = cumsum(start)) ->wc

```
Calculate Streak Length and Arrange

```{r}
wc %>%  group_by(rowid,streak_id) %>% 
  mutate(streak=row_number()) %>% 
  ungroup() %>% 
  arrange(.,rowid,DateEvent) %>% 
  rename(PreviousOutcome=lagged) -> wc
```

Previous Result

```{r}
wc %>% group_by(rowid) %>% mutate(StreakLength = lag(streak)) %>% 
  mutate(StreakLength = case_when(PreviousOutcome == 0 ~ -StreakLength, TRUE ~ StreakLength)) -> wc
```

Win Ratio

```{r}
wc %>% ungroup() %>% group_by(rowid) %>%  
  mutate(WinRatio = lag(cumsum(Outcome))/(row_number()-1)) %>% 
  mutate(CountFights =row_number()-1) ->wc
```

Finish Ratio and Finish Previous

```{r}
wc %>% mutate(FinishRatio = lag(!str_detect(Method,"Decision") & Outcome == 1)) %>%
  mutate(FinishRatio=replace_na(FinishRatio,FALSE)) %>% 
  mutate(FinishRatio = cumsum(FinishRatio)/(CountFights)) %>% 
  mutate(FinishPrevious = case_when(!str_detect(Method,"Decision") & Outcome == 1 ~TRUE, TRUE ~ FALSE)) %>% 
  mutate(FinishPrevious=lag(FinishPrevious)) -> wc
```

Finished Ratio and Finished Previous

```{r}
wc %>% mutate(FinishedRatio = lag(!str_detect(Method,"Decision") & Outcome == 0)) %>% mutate(FinishedRatio = replace_na(FinishedRatio,FALSE)) %>% 
  mutate(FinishedRatio = cumsum(FinishedRatio)/(CountFights)) %>% 
  mutate(FinishedPrevious = case_when(!str_detect(Method,"Decision") & Outcome == 0 ~TRUE, TRUE ~ FALSE)) %>% 
  mutate(FinishedPrevious = lag(FinishedPrevious)) -> wc
```

```{r}
wc %>% mutate(FinishedTrue = lag(!str_detect(Method,"Decision") & Outcome == 0)) %>% mutate(FinishedTrue = replace_na(FinishedTrue,FALSE)) %>% 
  mutate(FinishedCount=cumsum(FinishedTrue)) %>% 
  mutate(FinishTrue = lag(!str_detect(Method,"Decision") & Outcome == 1)) %>% mutate(FinishTrue = replace_na(FinishTrue,FALSE)) %>% 
  mutate(FinishCount=cumsum(FinishTrue)) %>% 
  mutate(DamageDiff = FinishCount/(FinishedCount+1)) %>% select(c(-FinishedTrue,-FinishTrue)) -> wc

```

```{r}
write.csv(wc,paste0(Sys.Date(),"_","results_cleaned.csv"))
```

Preparation for Results Matrix 

Join to Get Fighter Name

```{r}
wc %>% mutate(rowid = as.integer(rowid)) -> wx

div_lightweights %>% rename(Fighter = Opponent) -> div_lightweights

wx %>% left_join(div_lightweights,by="rowid") ->wx

wx %>% rename(Fighter=Fighter.y, Opponent=Fighter.x) -> wx

```

Reset for Opponent Id

```{r}
div_lightweights %>% rename(Opponent = Fighter) -> div_lightweights
```

Join For Opponent Id

```{r}
wx %>% left_join(div_lightweights,by="Opponent") -> wx

wx %>% rename(FighterId = rowid.x, OpponentId = rowid.y) -> wx

```
Remove Unnecessary Columns

```{r}
wx %>% select(-fighterName.x,-fighterName.y) -> wx
```

Join For Composite

```{r}
wx %>% mutate(FighterComposite = str_c(wx$FighterId,wx$Opponent,wx$DateEvent,sep = "_"),
              OpponentComposite =
                str_c(wx$OpponentId,wx$Fighter,wx$DateEvent,sep = "_")) ->wx 
```

Make Copies for Self Join
```{r}
wx -> wy
```


Join for Result Set

```{r}
wx %>% left_join(wy,by=c("FighterComposite"="OpponentComposite")) -> resultset
```

```{r}
write.csv(resultset,paste0(Sys.Date(),"_","resultset.csv"))
```

Unduplicate resultset

```{r}
resultset[!duplicated(resultset[c("Event.x","Round.x","Time.x","Method.x")]),] -> unduplicated_resultset
write.csv(unduplicated_resultset,paste0(Sys.Date(),"_","undup_resultset.csv"))
```


Filter down to reflect only complete cases

```{r}
unduplicated_resultset %>% filter(complete.cases(.)) -> modelset
write.csv(modelset,paste0(Sys.Date(),"_","modelset.csv"))
```


# Derive Odds
```{r}

```



Derived some more parameters
```{r}
modelset %>% mutate(delta_FP=FinishPrevious.x-FinishPrevious.y,
                    delta_FIP=FinishedPrevious.x-FinishedPrevious.y,
                    delta_FC=FinishCount.x-FinishCount.y,
                    delta_FIC=FinishedCount.x-FinishedCount.y) ->modelset_derived

write.csv(modelset_derived,paste0(Sys.Date(),"_","modelset_derived.csv"))
```

Define Dataset

```{r}
modelset_derived %>% select(Result.x,
                    Method.x,
                    Fighter.x,
                    Opponent.x,
                    CountFights.x,
                    PreviousOutcome.x,
                    StreakLength.x,
                    WinRatio.x,
                    FinishRatio.x,
                    FinishPrevious.x,
                    FinishedRatio.x,
                    FinishPrevious.x,
                    FinishCount.x,
                    FinishedCount.x,
                    DamageDiff.x,
                    CountFights.y,
                    PreviousOutcome.y,
                    StreakLength.y,
                    WinRatio.y,
                    FinishRatio.y,
                    FinishPrevious.y,
                    FinishedRatio.y,
                    FinishPrevious.y,
                    FinishCount.y,
                    FinishedCount.y,
                    DamageDiff.y,
                    delta_FP,
                    delta_FIP,
                    delta_FC,
                    delta_FIC) ->modelset_selected

write.csv(modelset_selected,paste0(Sys.Date(),"_","modelset_selected.csv"))
```

